%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% One Page Two Column Resume
% LaTeX Template
% Version 0.1
%
% Original author:
% SHLOK NANGIA
%
% Original repository:
% https://github.com/shloknangia/OnePageResume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[a4paper]{deedy-resume-openfont}
\usepackage{fancyhdr}
\RequirePackage[fixed]{fontawesome5}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{SHLOK}{NANGIA}{ % Your name
{\fontsize{15pt}{15pt}\fontspec[Path = fonts/lato/]{Lato-Lig}\selectfont Software Engineer \& Proud Geek}\\
%\urlstyle{same}\url{http://shloknangia.github.io} \\ % Your website, LinkedIn profile or other web address
{\faEnvelope}\href{mailto:shloknangia@gmail.com}{shloknangia@gmail.com} | {\faPhone}+91-9953055177 | {\faLinkedin}\href{https://www.linkedin.com/in/shloknangia/}{shloknangia} | {\faGithub}\href{https://github.com/shloknangia}{shloknangia}% Your contact information
}

%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%  \textbf{\href{http://shloknangia.github.io}{\fontsize{30pt}{30pt}\fontspec[Path = fonts/lato/]{Lato-Lig}\selectfont SHLOK \fontspec[Path = fonts/lato/]{Lato-Hai}\selectfont NANGIA}} & \href{mailto:shloknangia@gmail.com}{shloknangia@gmail.com}\\
%  \fontsize{15pt}{15pt}\fontspec[Path = fonts/lato/]{Lato-Lig}\selectfont SOFTWARE ENGINEER & +91-9953055177 \\
%\end{tabular*}
%\noindent\makebox[\linewidth]{\color{headings}\rule{\paperwidth}{0.4pt}}
% \vspace{-15pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Delhi Technological \\University (Formerly DCE)}
\descript{B. Tech Mathematics And Computing}
\location{July 2018 | Delhi, IN \\Aggregate: \textbf{81.2\%}}
\sectionsep

\subsection{New Green Field School}
\descript{AISSCE Class XII}
\location{2014 | Delhi, IN \\Percentage: \textbf{94.4 (100 \% in Mathematics)}}
\sectionsep

\subsection{New Green Field School}
\descript{AISSE Class X}
\location{2012 | Delhi, IN \\CGPA: \textbf{9.4}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Links} 
%Facebook:// \href{https://facebook/abc}{\bf dd} \\
%Github:// \href{https://github.com/abc}{\bf abc} \\
%LinkedIn://  \href{https://www.linkedin.com/in/abc}{\bf ABC} \\
%YouTube://  \href{https://www.youtube.com/user/abc}{\bf ABC \\
%Twitter://  \href{https://twitter.com/abc}{\bf @abc} \\
%Quora://  \href{https://www.quora.com/abc}{\bf ABC}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
% \subsection{Programming}
\location{Most Experience:}
Angular \textbullet{}   C++ \textbullet{} Python \textbullet{} Javascript \textbullet{}\\
Typescript \textbullet{} Git \textbullet{} VSTS \textbullet{} C \textbullet{} SQL \textbullet{}\\ 
Agile Development \textbullet{} HTML \textbullet{} CSS \textbullet{} \\
Bash \textbullet{} Data Structures \& Algo \\
\location{Some Experience:}
Java \textbullet{} .NET WEB API \textbullet{} Android SDK \textbullet{} Firebase \textbullet{} C\# \textbullet{} \LaTeX\  \\
\location{Familiar:}
MATLAB \textbullet{} SPSS 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{AWARDS}
% \subsection{Graduate}
\textbullet{} \location{First Position in Innovista Schlumberger
2020} -Schlumberger, PuTC \\
\textbullet{} \location{Reward of Excellence} -Schlumberger, PuTC \\
\textbullet{} \location{First Position in Data Ecosystem
Hackathon Schlumberger 2019} -Schlumberger, PuTC \\
\textbullet{} \location{Third Position in Data science
Hackathon 2019} -Schlumberger, PuTC \\
\textbullet{} \location{Merit certificate issued for scoring 100/100
marks in Mathematics in class XII} -Education Minister of Delhi \\
\textbullet{} \location{Best Academic Student of Science} -NGFS, Saket \\
%\location{Best Academic Student of Science
%Streame}  NGFS, Saket \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Volunteering
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\section{Volunteering}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightemize}
\textbullet{} Active member of \textbf{Schlumberger Empowerment Team}. \\
\textbullet{} Member of \textbf{Mathematics and Computing Society} of College (MACS). \\
\textbullet{} Actively participated as \textbf{Council Member} in School Council year 2012-13 (Class XI). \\
\textbullet{} Volunteered in a Project \textbf{“Helping youngsters to speak English”} in year 2010 - 2012 (Class IX \& X)
%\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{SCHLUMBERGER, PUTC}
\descript{| Software Engineer}
\location{May, 2018 – Current | Pune, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
 \item Developing Web applications for \textbf{Data monitoring and visualization} based on Angular 2+ framework and INT Geotoolkit to deliver \textbf{real-time drilling data} to clients.
 \item Designed and developed a responsive and \textbf{widget adaptable framework} which can be accessed on devices of all screen sizes i.e. Data visualization using widgets on Mobile devices
 \item Designed \& developed angular application using \textbf{Module Federation} approach to support UI Micro Frontends
 \item Tech Stack Using: Angular, .NET Web API and MongoDB
\end{tightemize}
\sectionsep

\runsubsection{BAR CODE INDIA LTD (BCIL)}
\descript{| Android Developer Intern}

\location{June, 2017 – July, 2017 | Faridabad, IN}
\begin{tightemize}
 \item Project on Android Based Application “Ride Share” where one could share its ride details and find a companion travelling in the same direction.
 \item All code was reviewed, perfected, and pushed to production.
 \item Tech Stack Using: JAVA, XML
\end{tightemize}
\sectionsep


\runsubsection{INFOTEL BUSINESS  LTD}
\descript{|  Android Developer Intern}
\location{December, 2016 – January, 2017 | Gurugram, IN}
\begin{tightemize}
 \item Front End Android Application Developer for their running Application WTC (Warranty Tracker And Checker).
 \item Tech Stack Using: JAVA, XML
\end{tightemize}
\sectionsep


\runsubsection{NHPC LIMITED}
\descript{|  Android Developer Intern}

\location{June, 2016 – July, 2016 | Faridabad, IN}
\begin{tightemize}
 \item Project on Android Based Employee Search System where one could search employee details based on the combination of 5 fields.
 \item Tech Stack Using: JAVA, XML
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{SMART SPEAKER}
% \descript{| Researcher}
\location{Jan 2014 – Jan 2015 | DTU, IN}
 A type of \textbf{wireless speaker} and voice command device with an integrated tools and services that offers \textbf{interactive actions and hands-free activation} with the help of one "hot word" (or several "hot words"). The key features were \textbf{solving mathematical expressions, real-time object detection and Image captioning}.
\begin{tightemize}
 \item Uses MatBot API (Also developed by Me) to \textbf{solve Mathematical Queries}.
 \item Developed an independent hardware using Raspberry Pi.
 \item Developed an\textbf{ interface between the hardware and software} using secure shell access through laptop and later configured to acceptinputs by buttons.
 \item Configured General Purpose Input/output pins on the raspberry pi which allowed to control the scripts by the simple press of a button.
 \item Added \textbf{Text-to-speech and Speech-to-Text} capability for visually impaired people.
\end{tightemize}
\sectionsep
%
\runsubsection{MATBOT}
% \descript{| Head Undergraduate Researcher}
\location{Jan 2014 – Jan 2015 | DTU, IN}
A python based assistant or bot which \textbf{solves mathematical expressions, interacts with a human} and support in their day-to-day tasks.
\begin{tightemize}
 \item developed Brain for MatBot using NLTK, Scikit on Python.
 \item exposed engine via \textbf{web service based on Flask framework}.
 \item developed MatBot interface on \textbf{Android mobile}.
\end{tightemize}
\sectionsep
%
\runsubsection{DTU CONNECT}
% \descript{| Head Undergraduate Researcher}
\location{Jan 2014 – Jan 2015 | DTU, IN}
\begin{tightemize}
 \item An Android application to find suitable \textbf{Blood Donors within the DTU Campus} in case of Accidents
 \item Used JSON format to store information about Blood Donors of DTU.
\end{tightemize}
\sectionsep

%\runsubsection{PORTFOLIO MANAGER}
%% \descript{| Head Undergraduate Researcher}
%% \location{Mar 2012 – May 2013 | Ithaca, NY}
%\begin{tightemize}
% \item An Android application to implement management of Stocks
% \item Used SQLite for database management.
% \item Shows current stock prices of Stocks with details.
%\end{tightemize}
%\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Publications} 
%\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
%\bibliographystyle{abbrv}
%\bibliography{publications}
%\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
